---
title: "MotionDiscrimEEGStats"
author: "Angela I Renton"
date: "08/06/2021"
output: html_document
---

## Description

These are the stats we ran on the main behavioural results for the motion descrimination task (pre vs. post training)

We start by loading in and organising our data. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load data, results = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(BayesFactor)
library(imager)


# load data
SSVEPdata = read.csv("//data.qbi.uq.edu.au/VISATTNNF-Q1357/Results/CompareSpaceFeat/group/motiondiscrim_SelectivityResults_ALL.csv")
SSVEPdata$SSVEP = SSVEPdata$Selectivity..Î.ÂµV.

#### step 1 - visualise the data 
# coplot(SSVEP ~ Attention.Trained |  Testday, data = SSVEPdata, panel = panel.smooth,
#        xlab = "Selectivity data: Selectivity vs attention trained, given testday")

#### Step 2 - create factors

SSVEPdata_orig = SSVEPdata

SSVEPdata$Attention.Trained = factor(SSVEPdata$Attention.Trained)
levels(SSVEPdata$Attention.Trained) = c( "Feature", "Sham", "Space")

SSVEPdata$NFTraining = SSVEPdata$Attention.Trained
levels(SSVEPdata$NFTraining) = c( "Neurofeedback", "Sham","Neurofeedback")

SSVEPdata$Attention.Type = factor(SSVEPdata$Attention.Type)
levels(SSVEPdata$Attention.Type) = c( "Feature", "Space")

SSVEPdata$Testday = factor(SSVEPdata$Testday)
levels(SSVEPdata$Testday) = c( "post-training", "pre-training")

SSVEPdata$SubID = factor(SSVEPdata$SubID)

## Step 3 - calculate training effects

idx_d1 = SSVEPdata$Testday=="pre-training"
idx_d4 = SSVEPdata$Testday=="post-training"

tmp_d1 = SSVEPdata[idx_d1,]
tmp_d4 = SSVEPdata[idx_d4,]

SSVEPdata_train = tmp_d1
SSVEPdata_train$SSVEP_TrEfct = tmp_d4$SSVEP - tmp_d1$SSVEP

```

## Define Functions
### We'll use these functions to run the analyses below

```{r Functions, include=FALSE}
DisplayANOVAResults2X2 <- function(formula, data, maineffectstringA, maineffectstringB) {
  bf = anovaBF(formula , data=data, whichRandom="SubID",  whichModels="all")
  bfInteraction = bf[7]/bf[4] # is the full model better than just strait main effects?
  bf_main_A = bf[7]/bf[5] # is the full model better than the main effect A knock out?
  bf_main_B = bf[7]/bf[6] # is the full model better than the main effect B knock out?
  
  
  # display results
  print(bf)
  cat('\n\nInteraction:\n\n')
  print(bfInteraction)
  
  cat(paste('\n\n', maineffectstringA, '\n\n'))
  print(bf_main_A)
  
  cat(paste('\n\n', maineffectstringB, '\n\n'))
  print(bf_main_B)
  
  return(bf)
}


followuptests <- function(formula, dataA, dataB) {
  bf = ttestBF(formula = formula, data = dataA)
  cat('\n\nNeurofeedback Group Pre Vs. Post\n\n')
  print(bf)
  
  cat('\n\nSham Group Pre Vs. Post\n\n')
  bf = ttestBF(formula = formula, data = dataB)
  print(bf)
}


Runstats_NFvsSham <- function(data, taskstring, measure) {
  # get data for measure and task
  datuse = data[data$Attention.Type %in% taskstring,]
  datuse["measure"] = datuse[measure]

  # get data for conditions of interest
  datuse_NF = datuse[datuse['NFTraining']=="Neurofeedback",]
  datuse_sham = datuse [datuse ['NFTraining']=="Sham",]
  
  # get Marginals
  dat = datuse%>% group_by(NFTraining, Testday)

  # run stats
  cat("ANOVA\n\n")
  bf = DisplayANOVAResults2X2(measure ~ NFTraining * Testday + SubID , data=datuse, maineffectstringA = "Neurofeedback Group:",         maineffectstringB = "Test Day:")

  # Run followup stats
  cat("\n\nFollowup Tests")
  followuptests(measure ~  Testday, dataA = datuse_NF, dataB = datuse_sham)

  return(dat)
}
  

```

```{r, include=FALSE}

followuptests2 <-function(data, formula){
  
  cat('\nSpace Cue \n')
  datuse = data[data['Attention.Type']=="Space",]
  cat('\nNF')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Neurofeedback",]))
  cat('\nSham')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Sham",]))
  cat('\nSpace')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Space",]))
  cat('\nFeat')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Feature",]))
  
  cat('\nFeat Cue \n')
  datuse = data[data['Attention.Type']=="Feature",]
  cat('\nNF')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Neurofeedback",]))
  cat('\nSham')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Sham",]))
  cat('\nSpace')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Space",]))
  cat('\nFeat')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Feature",]))
  
  cat('\nOverall \n')
  datuse = data
  cat('\nNF')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Neurofeedback",]))
  cat('\nSham')
  print(ttestBF(formula = formula, data = datuse[datuse['NFTraining']=="Sham",]))
  cat('\nSpace')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Space",]))
  cat('\nFeat')
  print(ttestBF(formula = formula, data = datuse[datuse['Attention.Trained']=="Feature",]))
}

followuptests3 <-function(data_train, formula1, formula2){
  
  cat('\nSpace Cue Training Effects \n')
  datuse = data_train[data_train['Attention.Type']=="Space",]
  
  cat('\nNF V Sham \n')
  print(ttestBF(formula = formula1, data = datuse))
  
  cat('\nSpace V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Space" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Space \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Space"),]
  levels(tmpdat$Attention.Trained) = c(1,1,2)
  print(ttestBF(formula = formula2 , data = tmpdat))

  
  
  cat('\nFeat Cue Training Effects \n')
  datuse = data_train[data_train['Attention.Type']=="Feature",]
  print(ttestBF(formula = formula1, data = datuse))
  
  cat('\nNF V Sham \n')
  print(ttestBF(formula = formula1, data = datuse))
  
  cat('\nSpace V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Space" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Space \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Space"),]
  levels(tmpdat$Attention.Trained) = c(1,1,2)
  print(ttestBF(formula = formula2 , data = tmpdat))

  
  
  cat('\nOverallTraining Effects \n')
  datuse = data_train
  print(ttestBF(formula = formula1, data = datuse))
  
  cat('\nNF V Sham \n')
  print(ttestBF(formula = formula1, data = datuse))
  
  cat('\nSpace V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Space" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Sham \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Sham"),]
  levels(tmpdat$Attention.Trained) = c(1,2,1)
  print(ttestBF(formula = formula2 , data = tmpdat))
  
  cat('\nFeature V Space \n')
  tmpdat = datuse[datuse$Attention.Trained %in% c("Feature" ,"Space"),]
  levels(tmpdat$Attention.Trained) = c(1,1,2)
  print(ttestBF(formula = formula2 , data = tmpdat))
}

  
```


## Question 1. Did the effect of training group on training effects differ by cuetype?(if so, we'll have to split up our analyses by cuetype)
### SSVEP Selectivity
```{r}
datuse_train = SSVEPdata_train
DisplayANOVAResults2X2(formula = SSVEP_TrEfct ~ NFTraining * Attention.Type + SubID , data=datuse_train, maineffectstringA = "Neurofeedback Group:", maineffectstringB = "Cue Type:")


```


## Question 2. What was the effect of training, and how did neurofeedback training effect these?

#### SSVEP Selectivity
for the space task, there was a training effect for the neurofeedback group but not the sham group
```{r}
# visualise result:
image = load.image(paste(direct.resultsRoot, "Motion Task SSVEP Selectivity training effect by attention.png", sep = ""))
plot(image, axes=FALSE)

# Run Stats
dat = Runstats_NFvsSham(SSVEPdata, taskstring = c('Space', 'Feature'), measure='SSVEPs')

# Marginals
cat("Marginals\n\n\n")
dat %>% summarise(M=mean(measure), SD=sd(measure))


followuptests3(SSVEPdata_train, SSVEP_TrEfct ~ NFTraining, SSVEP_TrEfct ~ Attention.Trained)

```

